Combinatorial interpretations of holonomic recurrences

### 2021-09-08 article/main.tex
Spellcheck

Up to today only a few interpretations of holonomic recurrences on trees have been found, including interpretation of holonomic recurrences for binary trees~\cite{binary}, unary-binary trees~\cite{motzkin}, and Schröder trees~\cite{schroder}. Unfortunately, the mentioned interpretations do not come with a method of finding them that could be generatlized to more complex cases.

@@

In Section~\ref{sec:introduction} we establish notation nad introduce concepts that will be used throughout the thesis.

@@

\begin{example}
    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisifies
    \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0.\]
\end{example}

@@

\begin{enumerate}
    \item Vro --- virtual leaf being right virtual-oneling;
    \item Vrt --- virtual leaf being right virtual-twinling. We will divide this case into:
        \begin{enumerate}
            \item VrtUrv --- Vri which uncle is a~right virtual leaf;
            \item VrtUra --- Vri which uncle is a~right actual node;
            \item VrtUla --- Vri which uncle is a~left actual node.
        \end{enumerate}
    \item Vlt --- virtual leaf left virtual-twinling. Note that from definition~\ref{def:unary_binary_2}, left virtual leave cannot have a~sibling being an~actual node. We can divide also this case into:
        \begin{enumerate}
            \item VltUrv --- Vlt which uncle is a~right virtual leaf;
            \item VltUra --- Vlt which uncle is a~right actual node;
            \item VltUla --- Vlt which uncle is a~left actual node;
        \end{enumerate}
    \item A --- Actual node.
\end{enumerate}

@@

You cannote that not every binary tree represents a~valid term.

@@

\begin{definition}
    Section \(T_{i,j}\) is defined as a~subset of \(T_i\) adding a~specific set of nodes. Webassign \(j\) according to the lexicographical order of lexicographically sorted node types.
\end{definition}

>>>>

Up to today only a few interpretations of holonomic recurrences on trees have been found, including interpretation of holonomic recurrences for binary trees~\cite{binary}, unary-binary trees~\cite{motzkin}, and Schröder trees~\cite{schroder}. Unfortunately, the mentioned interpretations do not come with a method of finding them that could be generalized to more complex cases.

@@

In Section~\ref{sec:introduction} we establish notation and introduce concepts that will be used throughout the thesis.

@@

\begin{example}
    The sequence \(a_n = \frac{5n - 3}{3n + 5}\) is holonomic, because it satisfies
    \[(3n + 5)(5n + 2) a_n - (5n - 3)(3n + 8) a_{n+1} = 0.\]
\end{example}

@@

\begin{enumerate}
    \item Vro --- virtual leaf being right virtual-oneling;
    \item Vrt --- virtual leaf being right virtual-twinling. We will divide this case into:
        \begin{enumerate}
            \item VrtUrv --- Vri which uncle is a~right virtual leaf;
            \item VrtUra --- Vri which uncle is a~right actual node;
            \item VrtUla --- Vri which uncle is a~left actual node.
        \end{enumerate}
    \item Vlt --- virtual leaf left virtual-twinling. Note that from definition~\ref{def:unary_binary_2}, left virtual leave cannot have a~sibling being an~actual node. We can divide also this case into:
        \begin{enumerate}
            \item VltUrv --- Vlt which uncle is a~right virtual leaf;
            \item VltUra --- Vlt which uncle is a~right actual node;
            \item VltUla --- Vlt which uncle is a~left actual node;
        \end{enumerate}
    \item A --- actual node.
\end{enumerate}

@@

You can note that not every binary tree represents a~valid term.

@@

\begin{definition}
    Section \(T_{i,j}\) is defined as a~subset of \(T_i\) adding a~specific set of nodes. We assign \(j\) according to the lexicographical order of lexicographically sorted node types.
\end{definition}
